\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-08 paper/paper.tex
New test results

\subsection{Experiment Setup}
For the testing, a single laptop was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.5 GHz and 8.00 GB) at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 6.6017 sec & 0.0048 sec & 0.0027 sec \\
hugecographs & >30 min & 29.8713 sec & 0.0214 sec \\
cycles175 & 13.7522 sec & 13.9265 sec & 0.0238 sec\\
bigtrees3 & 0.9652 sec & 0.2700 sec & 0.0323 sec\\
cubes6 & 0.5967 sec & 0.5877 sec & 0.0072 sec\\
products72 & 0.6083 sec & 0.6353 sec & 0.0123 sec\\
torus72 & 3.5590 sec & 3.6059 sec & 0.0106 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}

>>>>

\subsection{Experiment Setup}
For the testing, a single computer was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the computer was running Windows 10 Pro Technical Preview (at 3.75 GHz (average speed, max 3.9 GHz) and 8.00 GB) at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 6.6017 sec & 0.0048 sec & 0.0027 sec \\
hugecographs & >7 hours & 29.8713 sec & 0.0214 sec \\
cycles175 & 13.7522 sec & 13.9265 sec & 0.0238 sec\\
bigtrees3 & 0.9652 sec & 0.2700 sec & 0.0323 sec\\
cubes6 & 0.5967 sec & 0.5877 sec & 0.0072 sec\\
products72 & 0.6083 sec & 0.6353 sec & 0.0123 sec\\
torus72 & 3.5590 sec & 3.6059 sec & 0.0106 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
